\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-06-08 paper/ms.tex
tt
More RJObject writing

@@

\section{Specifying models in Julia}
Experimental support for model specification in the
\proglang{Julia} language is provided, with an example given in the
code/Templates/JuliaModel directory.
Set an enviroment variable {\tt JULIA\_LIB\_PATH} to the directory on your
system that contains the libraries {\tt libjulia.so} and
{\tt sys.so}. Set another environment variable {\tt JULIA\_INCLUDE\_PATH}
to the directory where the \proglang{Julia} header files are located
(do not include the final {\tt julia} directory in this path).

>>>>

To access the component parameters, the \code{RJObject} member function
\code{get_components} is used. This was used in the above functions, but more
typically it is needed in the log likelihood.
The member function \code{get_components} returns (by const reference) a
\code{std::vector} of \code{std::vector}s of \code{double}s. For example,
parameter two of component zero is:
\begin{CodeChunk}
\begin{CodeInput}
gaussians.get_components()[0][2]
\end{CodeInput}
\end{CodeChunk}
The order of $\{(\mu_j, \sigma_j, w_j)\}$
(i.e. which one is parameter 0, 1, and 2)
is determined by the conditional prior class, and is
explained in the following subsection.

\subsection{Conditional priors}

@@

\section{Specifying models in Julia}
Experimental support for model specification in the
\proglang{Julia} language is provided, with an example given in the
{\tt code/Templates/JuliaModel} directory.
Set an enviroment variable {\tt JULIA\_LIB\_PATH} to the directory on your
system that contains the libraries {\tt libjulia.so} and
{\tt sys.so}. Set another environment variable {\tt JULIA\_INCLUDE\_PATH}
to the directory where the \proglang{Julia} header files are located
(do not include the final {\tt julia} directory in this path).
